Data Pre-Processing

### 2021-08-06 AST-Framing-Ontario/Data Pre-Processesing.rmd
Create a raw policy corpus (not cleaned) to be used for kwic
New policy corpus created

@@

```{r}
save(academic_corpus, file= "Corpus .rda/academic_corpus.rda")
save(consortium_corpus, file= "Corpus .rda/consortium_corpus.rda")
save(municipal_corpus, file= "Corpus .rda/municipal_corpus.rda")
save(school_corpus, file= "Corpus .rda/school_corpus.rda")
save(policy_corpus, file= "Corpus .rda/policy_corpus.rda")
```

>>>>

## 3.4. Create corpus for concordances

Before removing stop words and punctuation, create a corpus to use for identifying keywords in context.

```{r}
raw_policy_corpus <- policy_corpus
```

@@

```{r}
save(academic_corpus, file= "Corpus .rda/academic_corpus.rda")
save(consortium_corpus, file= "Corpus .rda/consortium_corpus.rda")
save(municipal_corpus, file= "Corpus .rda/municipal_corpus.rda")
save(school_corpus, file= "Corpus .rda/school_corpus.rda")
save(policy_corpus, file= "Corpus .rda/policy_corpus.rda")
save(raw_policy_corpus, file= "Corpus .rda/raw_policy_corpus.rda")
```
